The Precambrian paleogeography of Laurentia

### 2020-09-17 Manuscript/pole_table.tex
updated pole table with Duluth paleolatitude column

\begin{longtable}{p{1 in}p{1 in}rrrrrrrr}
\toprule
                       terrane &                                        unit name & rating &  site lon &  site lat &  plon &  plat &  A\$\_\{95\}\$ &                    age &                                     pole reference \\
\midrule
\endhead
\midrule
\multicolumn{10}{r}{{Continued on next page}} \\
\midrule
\endfoot

@@

             Laurentia-Wyoming &                          Stillwater Complex - C2 &      A &     249.2 &      45.2 & 335.8 & -83.6 &       4.0 &     2705\$\textasciicircum \{+4\}\$\$\_\{-4\}\$ &                                 \textbackslash cite\{Selkin2008a\} \\
      Laurentia-Superior(East) &                     Otto Stock dykes and aureole &      B &     279.9 &      48.0 & 227.0 &  69.0 &       4.8 &     2676\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                               \textbackslash cite\{Pullaiah1975b\} \\
               Laurentia-Slave &                                     Defeat Suite &      B &     245.5 &      62.5 &  64.0 &  -1.0 &      15.0 &     2625\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                               \textbackslash cite\{Mitchell2014a\} \\
      Laurentia-Superior(East) &                       Ptarmigan-Mistassini dykes &      B &     287.0 &      54.0 & 213.0 & -45.3 &      13.8 &     2505\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                  \textbackslash cite\{Evans2010a\} \\
      Laurentia-Superior(East) &                               Matachewan dykes R &      A &     278.0 &      48.0 & 238.3 & -44.1 &       1.6 &   2466\$\textasciicircum \{+23\}\$\$\_\{-23\}\$ &                                  \textbackslash cite\{Evans2010a\} \\
      Laurentia-Superior(East) &                               Matachewan dykes N &      A &     278.0 &      48.0 & 239.5 & -52.3 &       2.4 &     2446\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &                                  \textbackslash cite\{Evans2010a\} \\
               Laurentia-Slave &                                     Malley dykes &      A &     249.8 &      64.2 & 310.0 & -50.8 &       6.7 &     2231\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                 \textbackslash cite\{Buchan2012a\} \\
      Laurentia-Superior(East) &                                 Senneterre dykes &      A &     283.0 &      49.0 & 284.3 & -15.3 &       5.5 &     2218\$\textasciicircum \{+6\}\$\$\_\{-6\}\$ &                                 \textbackslash cite\{Buchan1993a\} \\
      Laurentia-Superior(East) &                               Nipissing N1 sills &      A &     279.0 &      47.0 & 272.0 & -17.0 &      10.0 &     2217\$\textasciicircum \{+4\}\$\$\_\{-4\}\$ &                                 \textbackslash cite\{Buchan2000a\} \\
               Laurentia-Slave &                                     Dogrib dykes &      A &     245.5 &      62.5 & 315.0 & -31.0 &       7.0 &     2193\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                               \textbackslash cite\{Mitchell2014a\} \\
      Laurentia-Superior(East) &                                Biscotasing dykes &      A &     280.0 &      48.0 & 223.9 &  26.0 &       7.0 &     2170\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &                                  \textbackslash cite\{Evans2010a\} \\
             Laurentia-Wyoming &  Rabbit Creek, Powder River and South Path Dykes &      A &     252.8 &      43.9 & 339.2 &  65.5 &       7.6 &    2160\$\textasciicircum \{+11\}\$\$\_\{-8\}\$ &                                 \textbackslash cite\{Kilian2015a\} \\
               Laurentia-Slave &                                      Indin dykes &      A &     245.6 &      62.5 & 256.0 & -36.0 &       7.0 &    2126\$\textasciicircum \{+3\}\$\$\_\{-18\}\$ &                                 \textbackslash cite\{Buchan2016a\} \\
      Laurentia-Superior(West) &                                 Marathon dykes N &      A &     275.0 &      49.0 & 198.2 &  45.4 &       7.7 &     2124\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &                                  \textbackslash cite\{Halls2008a\} \\
      Laurentia-Superior(West) &                                 Marathon dykes R &      A &     275.0 &      49.0 & 182.2 &  55.1 &       7.5 &     2104\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &                                  \textbackslash cite\{Halls2008a\} \\
      Laurentia-Superior(West) &                               Cauchon Lake dykes &      A &     263.0 &      56.0 & 180.9 &  53.8 &       7.7 &     2091\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                  \textbackslash cite\{Evans2010a\} \\
      Laurentia-Superior(West) &                               Fort Frances dykes &      A &     266.0 &      48.0 & 184.6 &  42.8 &       6.1 &     2077\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                  \textbackslash cite\{Evans2010a\} \\
      Laurentia-Superior(East) &                                 Lac Esprit dykes &      A &     282.0 &      53.0 & 170.5 &  62.0 &       6.4 &     2069\$\textasciicircum \{+1\}\$\$\_\{-1\}\$ &                                  \textbackslash cite\{Evans2010a\} \\
      Laurentia-Greenland-Nain &                                  Kangamiut Dykes &      B &     307.0 &      66.0 & 273.8 &  17.1 &       2.7 &   2042\$\textasciicircum \{+12\}\$\$\_\{-12\}\$ &                                 \textbackslash cite\{Fahrig1976b\} \\
               Laurentia-Slave &                                Lac de Gras dykes &      A &     249.6 &      64.4 & 267.9 &  11.8 &       7.1 &     2026\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                 \textbackslash cite\{Buchan2009a\} \\
      Laurentia-Superior(East) &                                      Minto dykes &      A &     285.0 &      57.0 & 171.5 &  38.7 &      13.1 &     1998\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                  \textbackslash cite\{Evans2010a\} \\
               Laurentia-Slave &                                  Rifle Formation &      B &     252.9 &      65.9 & 341.0 &  14.0 &       7.7 &     1963\$\textasciicircum \{+6\}\$\$\_\{-6\}\$ &                                  \textbackslash cite\{Evans1981a\} \\
                 Laurentia-Rae &                           Clearwater Anorthosite &      B &     251.6 &      57.1 & 311.8 &   6.5 &       2.9 &     1917\$\textasciicircum \{+7\}\$\$\_\{-7\}\$ &                                  \textbackslash cite\{Halls1999a\} \\
             Laurentia-Wyoming &                       Sourdough mafic dike swarm &      A &    -108.3 &      44.7 & 292.0 &  49.2 &       8.1 &     1899\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                 \textbackslash cite\{Kilian2016b\} \\
               Laurentia-Slave &                                 Ghost Dike Swarm &      A &     244.6 &      62.6 & 286.0 &  -2.0 &       6.0 &     1887\$\textasciicircum \{+5\}\$\$\_\{-9\}\$ &                                 \textbackslash cite\{Buchan2016a\} \\
               Laurentia-Slave &                         Mean Seton/Akaitcho/Mara &      B &     250.0 &      65.0 & 260.0 &  -6.0 &       4.0 &     1885\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                               \textbackslash cite\{Mitchell2010c\} \\
               Laurentia-Slave &                   Mean Kahochella, Peacock Hills &      B &     250.0 &      65.0 & 285.0 & -12.0 &       7.0 &     1882\$\textasciicircum \{+4\}\$\$\_\{-4\}\$ &                               \textbackslash cite\{Mitchell2010c\} \\
      Laurentia-Superior(West) &                              Molson (B+C2) dykes &      A &     262.0 &      55.0 & 218.0 &  28.9 &       3.8 &     1879\$\textasciicircum \{+6\}\$\$\_\{-6\}\$ &                                  \textbackslash cite\{Evans2010a\} \\
               Laurentia-Slave &        Douglas Peninsula Formation, Pethei Group &      B &     249.7 &      62.8 & 258.0 & -18.0 &      14.2 &   1876\$\textasciicircum \{+10\}\$\$\_\{-10\}\$ &                                 \textbackslash cite\{Irving1979a\} \\
               Laurentia-Slave &                               Takiyuak Formation &      B &     246.9 &      66.1 & 249.0 & -13.0 &       8.0 &   1876\$\textasciicircum \{+10\}\$\$\_\{-10\}\$ &                                 \textbackslash cite\{Irving1979a\} \\
            Laurentia-Superior &                       Haig/Flaherty/Sutton Mean  &      B &     279.0 &      56.0 & 245.8 &   1.0 &       3.9 &     1870\$\textasciicircum \{+1\}\$\$\_\{-1\}\$ &  Nordic workshop calculation based on data of \textbackslash ... \\
               Laurentia-Slave &             Pearson A/Peninsular/Kilohigok sills &      A &     250.0 &      65.0 & 269.0 & -22.0 &       6.0 &     1870\$\textasciicircum \{+4\}\$\$\_\{-4\}\$ &                               \textbackslash cite\{Mitchell2010c\} \\
 Laurentia-Trans-Hudson orogen &                              Boot-Phantom Pluton &      B &     258.1 &      54.7 & 275.4 &  62.4 &       7.9 &     1838\$\textasciicircum \{+1\}\$\$\_\{-1\}\$ &                                 \textbackslash cite\{Symons1999a\} \\
                 Laurentia-Rae &                                    Sparrow Dykes &      B &     250.2 &      61.6 & 291.0 &  12.0 &       7.9 &     1827\$\textasciicircum \{+4\}\$\$\_\{-4\}\$ &                                \textbackslash cite\{McGlynn1974a\} \\
                 Laurentia-Rae &                                 Martin Formation &      A &     251.4 &      59.6 & 288.0 &  -9.0 &       8.5 &     1818\$\textasciicircum \{+4\}\$\$\_\{-4\}\$ &                                  \textbackslash cite\{Evans1973a\} \\
                     Laurentia &                                    Dubawnt Group &      B &     265.6 &      64.1 & 277.0 &   7.0 &       8.0 &   1785\$\textasciicircum \{+35\}\$\$\_\{-35\}\$ &                                   \textbackslash cite\{Park1973a\} \\
 Laurentia-Trans-Hudson orogen &                          Deschambault Pegmatites &      B &     256.7 &      54.9 & 276.0 &  67.5 &       7.7 &     1766\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                 \textbackslash cite\{Symons2000a\} \\
 Laurentia-Trans-Hudson orogen &                                 Jan Lake Granite &      B &     257.2 &      54.9 & 264.3 &  24.3 &      16.9 &     1758\$\textasciicircum \{+1\}\$\$\_\{-1\}\$ &                                   \textbackslash cite\{Gala1995a\} \\
                     Laurentia &                                    Cleaver Dykes &      A &     242.0 &      67.5 & 276.7 &  19.4 &       6.1 &     1741\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                 \textbackslash cite\{Irving2004a\} \\
           Laurentia-Greenland &                      Melville Bugt diabase dykes &      B &     303.0 &      74.6 & 273.8 &   5.0 &       8.7 &     1633\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                  \textbackslash cite\{Halls2011a\} \\
                     Laurentia &                          Western Channel Diabase &      A &     242.2 &      66.4 & 245.0 &   9.0 &       6.6 &     1590\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &                                 \textbackslash cite\{Irving1972a\} \\
                     Laurentia &               St.Francois Mountains Acidic Rocks &      A &     269.5 &      37.5 & 219.0 & -13.2 &       6.1 &   1476\$\textasciicircum \{+16\}\$\$\_\{-16\}\$ &                                  \textbackslash cite\{Meert2002b\} \\
                     Laurentia &                             Michikamau Intrusion &      A &     296.0 &      54.5 & 217.5 &  -1.5 &       4.7 &     1460\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                 \textbackslash cite\{Emslie1976a\} \\
                     Laurentia &                                Spokane Formation &      A &     246.8 &      48.2 & 215.5 & -24.8 &       4.7 &   1458\$\textasciicircum \{+13\}\$\$\_\{-13\}\$ &                                 \textbackslash cite\{Elston2002a\} \\
                     Laurentia &                               Snowslip Formation &      A &     245.9 &      47.9 & 210.2 & -24.9 &       3.5 &   1450\$\textasciicircum \{+14\}\$\$\_\{-14\}\$ &                                 \textbackslash cite\{Elston2002a\} \\
                     Laurentia &                               Tobacco Root dykes &      B &     247.6 &      47.4 & 216.1 &   8.7 &      10.5 &   1448\$\textasciicircum \{+49\}\$\$\_\{-49\}\$ &                                 \textbackslash cite\{Harlan2008a\} \\
                     Laurentia &                                     Purcell Lava &      A &     245.1 &      49.4 & 215.6 & -23.6 &       4.8 &     1443\$\textasciicircum \{+7\}\$\$\_\{-7\}\$ &                                 \textbackslash cite\{Elston2002a\} \\
                     Laurentia &                        Rocky Mountain intrusions &      B &     253.8 &      40.3 & 217.4 & -11.9 &       9.7 &   1430\$\textasciicircum \{+15\}\$\$\_\{-15\}\$ &  Nordic workshop calculation based on data of \textbackslash ... \\
                     Laurentia &                                 Mistastin Pluton &      B &     296.3 &      55.6 & 201.5 &  -1.0 &       7.6 &   1425\$\textasciicircum \{+25\}\$\$\_\{-25\}\$ &                                 \textbackslash cite\{Fahrig1976a\} \\
                     Laurentia &                               McNamara Formation &      A &     246.4 &      46.9 & 208.3 & -13.5 &       6.7 &     1401\$\textasciicircum \{+6\}\$\$\_\{-6\}\$ &                                 \textbackslash cite\{Elston2002a\} \\
                     Laurentia &       Pilcher, Garnet Range and Libby Formations &      A &     246.4 &      46.7 & 215.3 & -19.2 &       7.7 &   1385\$\textasciicircum \{+23\}\$\$\_\{-23\}\$ &                                 \textbackslash cite\{Elston2002a\} \\
           Laurentia-Greenland &                              Zig-Zag Dal Basalts &      B &     334.8 &      81.2 & 242.8 &  12.0 &       3.8 &     1382\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                              \textbackslash cite\{Marcussen1983a\} \\
           Laurentia-Greenland &                    Victoria Fjord dolerite dykes &      B &     315.3 &      81.5 & 231.7 &  10.3 &       4.3 &     1382\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                             \textbackslash cite\{Abrahamsen1987a\} \\
           Laurentia-Greenland &                            Midsommersoe Dolerite &      B &     333.4 &      81.6 & 242.0 &   6.9 &       5.1 &     1382\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                              \textbackslash cite\{Marcussen1983a\} \\
                     Laurentia &                                 Nain Anorthosite &      B &     298.2 &      56.5 & 206.7 &  11.7 &       2.2 &   1305\$\textasciicircum \{+15\}\$\$\_\{-15\}\$ &                                 \textbackslash cite\{Murthy1978a\} \\
           Laurentia-Greenland &                                Kungnat Ring Dyke &      B &     311.7 &      61.2 & 198.7 &   3.4 &       3.2 &     1275\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                  \textbackslash cite\{Piper1977b\} \\
           Laurentia-Greenland &                           North Qoroq intrusives &      B &     314.6 &      61.1 & 202.6 &  13.2 &       8.3 &     1275\$\textasciicircum \{+1\}\$\$\_\{-1\}\$ &                                  \textbackslash cite\{Piper1992a\} \\
                     Laurentia &                       Mackenzie dykes grand mean &      A &     250.0 &      65.0 & 190.0 &   4.0 &       5.0 &     1267\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &                                 \textbackslash cite\{Buchan2000a\} \\
           Laurentia-Greenland &                       West Gardar Dolerite Dykes &      B &     311.7 &      61.2 & 201.7 &   8.7 &       6.6 &     1244\$\textasciicircum \{+8\}\$\$\_\{-8\}\$ &                                  \textbackslash cite\{Piper1977b\} \\
           Laurentia-Greenland &                    West Gardar Lamprophyre Dykes &      B &     311.7 &      61.2 & 206.4 &   3.2 &       7.2 &   1238\$\textasciicircum \{+11\}\$\$\_\{-11\}\$ &                                  \textbackslash cite\{Piper1977b\} \\
                     Laurentia &                           Sudbury Dykes Combined &      A &     278.6 &      46.3 & 192.8 &  -2.5 &       2.5 &     1237\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &                                 \textbackslash cite\{Palmer1977a\} \\
            Laurentia-Scotland &                                      Stoer Group &      B &     354.5 &      58.0 & 238.4 &  37.2 &       7.7 &   1199\$\textasciicircum \{+70\}\$\$\_\{-70\}\$ &                        Nordic workshop calculation \\

>>>>

\begin{longtable}{p{1 in}p{1 in}rrrrrrrr}
\toprule
                       terrane &                                          unit name &                    age & rating &  site lon &  site lat &  plon &  plat &  A\$\_\{95\}\$ &  Duluth lat &                                     pole reference \\
\midrule
\endhead
\midrule
\multicolumn{11}{r}{{Continued on next page}} \\
\midrule
\endfoot

@@

             Laurentia-Wyoming &                            Stillwater Complex - C2 &     2705\$\textasciicircum \{+4\}\$\$\_\{-4\}\$ &      A &     249.2 &      45.2 & 335.8 & -83.6 &       4.0 &         nan &                                 \textbackslash cite\{Selkin2008a\} \\
  Baltica-Fennoscandia-Karelia &                                Koitere sanukitoids &     2684\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &      B &      30.6 &      63.3 & 192.5 & -67.5 &      19.5 &         nan &                                                NaN \\
      Laurentia-Superior(East) &                       Otto Stock dikes and aureole &     2676\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &      B &     279.9 &      48.0 & 227.0 &  69.0 &       4.8 &         nan &                               \textbackslash cite\{Pullaiah1975b\} \\
               Laurentia-Slave &                                       Defeat Suite &     2625\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &      B &     245.5 &      62.5 &  64.0 &  -1.0 &      15.0 &         nan &                               \textbackslash cite\{Mitchell2014a\} \\
          Baltica-Fennoscandia &                   Shalskiy thick gabbronorite dike &     2511\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &      B &      36.0 &      61.9 & 222.1 &  22.7 &      11.5 &         nan &                                                NaN \\
      Laurentia-Superior(East) &                         Ptarmigan-Mistassini dikes &     2505\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &      B &     287.0 &      54.0 & 213.0 & -45.3 &      13.8 &         nan &                                  \textbackslash cite\{Evans2010a\} \\
          Baltica-Fennoscandia &                     Generalskaya Layered Intrusion &     2505\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &      B &      31.0 &      69.4 & 292.7 & -42.5 &      10.4 &         nan &                                                NaN \\
          Baltica-Fennoscandia &                              Monchegorsk Intrusion &     2504\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &      B &      33.0 &      68.0 & 265.3 &   1.3 &       9.9 &         nan &                                                NaN \\
          Baltica-Fennoscandia &  Avdeev gabbronorite and thin Shalskiy diabase ... &   2476\$\textasciicircum \{+35\}\$\$\_\{-35\}\$ &      B &      36.0 &      61.9 & 243.5 & -12.3 &      14.0 &         nan &                                                NaN \\
      Laurentia-Superior(East) &                                 Matachewan dikes R &   2466\$\textasciicircum \{+23\}\$\$\_\{-23\}\$ &      A &     278.0 &      48.0 & 238.3 & -44.1 &       1.6 &         nan &                                  \textbackslash cite\{Evans2010a\} \\
          Baltica-Fennoscandia &                          Imandra Layered Intrusion &   2446\$\textasciicircum \{+39\}\$\$\_\{-39\}\$ &      B &      33.1 &      67.6 & 280.3 & -16.1 &       7.8 &         nan &                                                NaN \\
          Baltica-Fennoscandia &                                     Karelian dikes &     2446\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &      B &      30.7 &      66.0 & 278.7 & -19.9 &       6.1 &         nan &                                                NaN \\
      Laurentia-Superior(East) &                                 Matachewan dikes N &     2446\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &      A &     278.0 &      48.0 & 239.5 & -52.3 &       2.4 &         nan &                                  \textbackslash cite\{Evans2010a\} \\
          Baltica-Fennoscandia &                            Taivalkoski 2.3 Ga dike &   2339\$\textasciicircum \{+18\}\$\$\_\{-18\}\$ &     C+ &      28.1 &      65.5 & 257.3 &  20.4 &       6.3 &         nan &                                                NaN \\
               Laurentia-Slave &                                       Malley dikes &     2231\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &      A &     249.8 &      64.2 & 310.0 & -50.8 &       6.7 &         nan &                                 \textbackslash cite\{Buchan2012a\} \\
      Laurentia-Superior(East) &                                   Senneterre dikes &     2218\$\textasciicircum \{+6\}\$\$\_\{-6\}\$ &      A &     283.0 &      49.0 & 284.3 & -15.3 &       5.5 &         nan &                                 \textbackslash cite\{Buchan1993a\} \\
      Laurentia-Superior(East) &                                 Nipissing N1 sills &     2217\$\textasciicircum \{+4\}\$\$\_\{-4\}\$ &      A &     279.0 &      47.0 & 272.0 & -17.0 &      10.0 &         nan &                                 \textbackslash cite\{Buchan2000a\} \\
               Laurentia-Slave &                                       Dogrib dikes &     2193\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &      A &     245.5 &      62.5 & 315.0 & -31.0 &       7.0 &         nan &                               \textbackslash cite\{Mitchell2014a\} \\
      Laurentia-Superior(East) &                                  Biscotasing dikes &     2170\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &      A &     280.0 &      48.0 & 223.9 &  26.0 &       7.0 &         nan &                                  \textbackslash cite\{Evans2010a\} \\
             Laurentia-Wyoming &    Rabbit Creek, Powder River and South Path dikes &    2160\$\textasciicircum \{+11\}\$\$\_\{-8\}\$ &      A &     252.8 &      43.9 & 339.2 &  65.5 &       7.6 &         nan &                                 \textbackslash cite\{Kilian2015a\} \\
               Laurentia-Slave &                                        Indin dikes &    2126\$\textasciicircum \{+3\}\$\$\_\{-18\}\$ &      A &     245.6 &      62.5 & 256.0 & -36.0 &       7.0 &         nan &                                 \textbackslash cite\{Buchan2016a\} \\
      Laurentia-Superior(West) &                                   Marathon dikes N &     2124\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &      A &     275.0 &      49.0 & 198.2 &  45.4 &       7.7 &        43.3 &                                  \textbackslash cite\{Halls2008a\} \\
      Laurentia-Superior(West) &                                   Marathon dikes R &     2104\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &      A &     275.0 &      49.0 & 182.2 &  55.1 &       7.5 &        38.8 &                                  \textbackslash cite\{Halls2008a\} \\
      Laurentia-Superior(West) &                                 Cauchon Lake dikes &     2091\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &      A &     263.0 &      56.0 & 180.9 &  53.8 &       7.7 &        37.5 &                                  \textbackslash cite\{Evans2010a\} \\
      Laurentia-Superior(West) &                                 Fort Frances dikes &     2077\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &      A &     266.0 &      48.0 & 184.6 &  42.8 &       6.1 &        33.6 &                                  \textbackslash cite\{Evans2010a\} \\
      Laurentia-Superior(East) &                                   Lac Esprit dikes &     2069\$\textasciicircum \{+1\}\$\$\_\{-1\}\$ &      A &     282.0 &      53.0 & 170.5 &  62.0 &       6.4 &         nan &                                  \textbackslash cite\{Evans2010a\} \\
              Baltica-Sarmatia &               Volyn-Dniestr-Bug intrusions A-group &   2061\$\textasciicircum \{+20\}\$\$\_\{-20\}\$ &      B &      29.8 &      49.6 & 182.9 &  15.7 &      13.7 &         nan &                                                NaN \\
          Baltica-Fennoscandia &                               Kuetsyarvi Formation &     2060\$\textasciicircum \{+8\}\$\$\_\{-8\}\$ &      B &      29.5 &      69.5 & 300.8 &  24.7 &      16.4 &         nan &                                                NaN \\
      Laurentia-Greenland-Nain &                                    Kangamiut dikes &   2042\$\textasciicircum \{+12\}\$\$\_\{-12\}\$ &      B &     307.0 &      66.0 & 273.8 &  17.1 &       2.7 &        57.6 &                                 \textbackslash cite\{Fahrig1976b\} \\
               Laurentia-Slave &                                  Lac de Gras dikes &     2026\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &      A &     249.6 &      64.4 & 267.9 &  11.8 &       7.1 &         nan &                                 \textbackslash cite\{Buchan2009a\} \\
              Baltica-Sarmatia &                       Volyn-Dniestr-Bug intrusions &   2000\$\textasciicircum \{+10\}\$\$\_\{-10\}\$ &      B &      27.4 &      50.9 & 140.4 &  64.4 &      12.7 &         nan &                                                NaN \\
      Laurentia-Superior(East) &                                        Minto dikes &     1998\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &      A &     285.0 &      57.0 & 171.5 &  38.7 &      13.1 &         nan &                                  \textbackslash cite\{Evans2010a\} \\
             Baltica - Karelia &                           Onego 1975 Ma Intrusions &     1976\$\textasciicircum \{+9\}\$\$\_\{-9\}\$ &      A &      34.0 &      62.1 & 101.5 &  44.4 &       6.3 &         nan &                                                NaN \\
          Baltica-Fennoscandia &                                    Konchozero Sill &   1974\$\textasciicircum \{+27\}\$\$\_\{-27\}\$ &      B &      34.0 &      62.1 & 281.9 & -14.2 &      10.4 &         nan &                                                NaN \\
               Laurentia-Slave &                                    Rifle Formation &     1963\$\textasciicircum \{+6\}\$\$\_\{-6\}\$ &      B &     252.9 &      65.9 & 341.0 &  14.0 &       7.7 &         nan &                                  \textbackslash cite\{Evans1981a\} \\
          Baltica-Fennoscandia &             Tsuomasavarri Gabbro-Diorite Intrusion &     1931\$\textasciicircum \{+2\}\$\$\_\{-2\}\$ &      B &      28.3 &      69.9 & 247.3 &  40.2 &       6.0 &         nan &                                                NaN \\
                 Laurentia-Rae &                             Clearwater Anorthosite &     1917\$\textasciicircum \{+7\}\$\$\_\{-7\}\$ &      B &     251.6 &      57.1 & 311.8 &   6.5 &       2.9 &         nan &                                  \textbackslash cite\{Halls1999a\} \\
             Laurentia-Wyoming &                         Sourdough mafic dike swarm &     1899\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &      A &    -108.3 &      44.7 & 292.0 &  49.2 &       8.1 &         nan &                                 \textbackslash cite\{Kilian2016b\} \\
               Laurentia-Slave &                                   Ghost Dike Swarm &     1887\$\textasciicircum \{+5\}\$\$\_\{-9\}\$ &      A &     244.6 &      62.6 & 286.0 &  -2.0 &       6.0 &         nan &                                 \textbackslash cite\{Buchan2016a\} \\
          Baltica-Fennoscandia &                         Kiuruvesi-Pielavesi gabbro &     1886\$\textasciicircum \{+6\}\$\$\_\{-5\}\$ &      B &      26.8 &      63.2 & 231.3 &  41.1 &       5.4 &         nan &                                                NaN \\
               Laurentia-Slave &                           Mean Seton/Akaitcho/Mara &     1885\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &      B &     250.0 &      65.0 & 260.0 &  -6.0 &       4.0 &         nan &                               \textbackslash cite\{Mitchell2010c\} \\
               Laurentia-Slave &                     Mean Kahochella, Peacock Hills &     1882\$\textasciicircum \{+4\}\$\$\_\{-4\}\$ &      B &     250.0 &      65.0 & 285.0 & -12.0 &       7.0 &         nan &                               \textbackslash cite\{Mitchell2010c\} \\
      Laurentia-Superior(West) &                                Molson (B+C2) dikes &     1879\$\textasciicircum \{+6\}\$\$\_\{-6\}\$ &      A &     262.0 &      55.0 & 218.0 &  28.9 &       3.8 &        47.6 &                                  \textbackslash cite\{Evans2010a\} \\
               Laurentia-Slave &                                 Takiyuak Formation &   1876\$\textasciicircum \{+10\}\$\$\_\{-10\}\$ &      B &     246.9 &      66.1 & 249.0 & -13.0 &       8.0 &         nan &                                 \textbackslash cite\{Irving1979a\} \\
               Laurentia-Slave &          Douglas Peninsula Formation, Pethei Group &   1876\$\textasciicircum \{+10\}\$\$\_\{-10\}\$ &      B &     249.7 &      62.8 & 258.0 & -18.0 &      14.2 &         nan &                                 \textbackslash cite\{Irving1979a\} \\
               Laurentia-Slave &               Pearson A/Peninsular/Kilohigok sills &     1870\$\textasciicircum \{+4\}\$\$\_\{-4\}\$ &      A &     250.0 &      65.0 & 269.0 & -22.0 &       6.0 &         nan &                               \textbackslash cite\{Mitchell2010c\} \\
            Laurentia-Superior &                         Haig/Flaherty/Sutton Mean  &     1870\$\textasciicircum \{+1\}\$\$\_\{-1\}\$ &      B &     281.0 &      56.2 & 245.8 &   1.0 &       3.9 &         nan &  Nordic workshop calculation based on data of \textbackslash ... \\
        Baltica - Fennoscandia &                                      Keuruu dikes  &   1869\$\textasciicircum \{+10\}\$\$\_\{-10\}\$ &     B  &      24.7 &      62.3 & 230.9 &  45.7 &       5.5 &         nan &                                                NaN \\
 Laurentia-Trans-Hudson orogen &                                Boot-Phantom Pluton &     1838\$\textasciicircum \{+1\}\$\$\_\{-1\}\$ &      B &     258.1 &      54.7 & 275.4 &  62.4 &       7.9 &        73.8 &                                 \textbackslash cite\{Symons1999a\} \\
                 Laurentia-Rae &                                      Sparrow dikes &     1827\$\textasciicircum \{+4\}\$\$\_\{-4\}\$ &      B &     250.2 &      61.6 & 291.0 &  12.0 &       7.9 &         nan &                                \textbackslash cite\{McGlynn1974a\} \\
                 Laurentia-Rae &                                   Martin Formation &     1818\$\textasciicircum \{+4\}\$\$\_\{-4\}\$ &      A &     251.4 &      59.6 & 288.0 &  -9.0 &       8.5 &         nan &                                  \textbackslash cite\{Evans1973a\} \\
          Baltica-Fennoscandia &                                    Notträsk gabbro &     1806\$\textasciicircum \{+6\}\$\$\_\{-6\}\$ &      B &      21.8 &      65.8 & 216.2 &  43.5 &       6.1 &         nan &                                                NaN \\
          Baltica-Fennoscandia &                                      Kallax gabbro &     1800\$\textasciicircum \{+5\}\$\$\_\{-6\}\$ &      B &      22.0 &      65.5 & 209.0 &  49.0 &       nan &         nan &                                                NaN \\
          Baltica-Fennoscandia &                 Lake Ladoga, Mean intr. \& dikes, A &   1800\$\textasciicircum \{+19\}\$\$\_\{-56\}\$ &      B &      30.0 &      61.3 & 229.1 &  50.9 &       nan &         nan &                                                NaN \\
          Baltica-Fennoscandia &                                      Hoting gabbro &   1786\$\textasciicircum \{+10\}\$\$\_\{-10\}\$ &      A &      16.2 &      64.2 & 233.3 &  43.0 &      10.9 &         nan &                                                NaN \\
                     Laurentia &                                      Dubawnt Group &   1785\$\textasciicircum \{+35\}\$\$\_\{-35\}\$ &      B &     265.6 &      64.1 & 277.0 &   7.0 &       8.0 &        49.4 &                                   \textbackslash cite\{Park1973a\} \\
          Baltica-Fennoscandia &                              Småland intrusives -C &     1777\$\textasciicircum \{+8\}\$\$\_\{-8\}\$ &      A &      15.7 &      57.1 & 182.7 &  45.7 &       8.0 &         nan &                                                NaN \\
          Baltica-Fennoscandia &                                 Shoksha Sandstones &   1775\$\textasciicircum \{+25\}\$\$\_\{-25\}\$ &      B &      33.8 &      61.3 & 221.1 &  39.7 &       4.0 &         nan &                                                NaN \\
 Laurentia-Trans-Hudson orogen &                            Deschambault Pegmatites &     1766\$\textasciicircum \{+5\}\$\$\_\{-5\}\$ &      B &     256.7 &      54.9 & 276.0 &  67.5 &       7.7 &        68.9 &                                 \textbackslash cite\{Symons2000a\} \\
 Laurentia-Trans-Hudson orogen &                                   Jan Lake Granite &     1758\$\textasciicircum \{+1\}\$\$\_\{-1\}\$ &      B &     257.2 &      54.9 & 264.3 &  24.3 &      16.9 &        67.3 &                                   \textbackslash cite\{Gala1995a\} \\
              Baltica-Sarmatia &                       Volyn-Dniestr-Bug intrusions &   1755\$\textasciicircum \{+15\}\$\$\_\{-15\}\$ &      A &      28.6 &      50.6 & 169.1 &  26.5 &       3.9 &         nan &                                                NaN \\
          Baltica-Fennoscandia &                                MEAN Ropruchey sill &     1751\$\textasciicircum \{+3\}\$\$\_\{-3\}\$ &      B &      35.3 &      61.4 & 217.0 &  39.1 &       8.6 &         nan &                                                NaN \\
